Adding Sensitivity to 21cm Inteferometric Probes of Reionization by Optimizing Choice of Baselines

### 2017-03-04 Rotation paper/draft_working.tex
save

The earth's rotation causes the baselines to pick up different modes of the sky with time. 
This effect is used extensively to improve uv coverage in imaging with minimum redundancy arrays. In
a maximally redundant array, baselines that are slightly different
rotate into each other at a time delay. Here we present a method to
improve the sensitivity of the maximum redundancy arrays by including
the uv redundancy of different baselines at a time lag.

@@

\subsection{Validation with PAPER-128 Data}
Unlike the simulated clean EOR signal, real data are dominated by foreground and thermal noise, neither of which turns out to exhibit the correlation pattern seen in Fig.  \ref{fig:numerics}. Foreground exhibits long-range correlations and would lead to high responses at wide range of time-offsets. Instrumental noise fo different baselines/antenna-pairs, on the other hand, are uncorrelated and thus exhibit responses consistent with zero at all time offsets.

@@

\bibliographystyle{apj}
%\nocite{*}
\bibliography{draft_working}

>>>>

The earth's rotation causes the baselines to pick up different modes of the sky with time. 
This effect is used extensively to improve uv coverage in imaging with minimum redundancy arrays. In
a maximally redundant array, baselines that are slightly different
rotate into each other at a time delay. Here we present a method to
improve the sensitivity of the maximum redundancy arrays by including
the uv redundancy of different baselines at a time lag. It's worth noting 
as recent progress the authors of \cite{wterm} proposes an algorithmic search approach to extract information from near-equivalent baselines. We here propose a simple and elegant theoretical formalism that in addition allows us to identify baselines to cross-correlate and predict the weight of sensitivity.

@@

\subsection{Notes on Data, Foreground and Noise}
Unlike the simulated clean EOR signal, real data are dominated by foreground and thermal noise, neither of which turns out to exhibit the correlation pattern seen in Fig.  \ref{fig:numerics}. Foreground exhibits long-range correlations and would lead to high responses at wide range of time-offsets. Instrumental noise for different baselines/antenna-pairs, on the other hand, are uncorrelated and thus exhibit responses consistent with zero at all time offsets. 
To illustrate, we use the second observing season of PAPER-128 data, taken from Jan. 21st to March 7th of 2014. To illustrate the effect of noise and foreground, we use the data before fringe-rate and delay filtering.

@@

\appendix
\section{\\Hera Analysis}
\begin{widetext}
\begin{figure}[H]
\includegraphics[scale=0.55]{HeraAntpos}

\caption{Planned Hydrogen Epoch of Reionization Array antenna configurations\label{fig:HeraAntpos}}
\end{figure}
\end{widetext}
\bibliographystyle{apj}
%\nocite{*}
\bibliography{draft_working}
